%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Assistant Conductor of Concert Band} % Affiliation/role
    {Colorado School of Mines Music Department} % Organization/group
    {Golden, Colorado, USA} % Location
    {2013 - 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Conducted over 80 students to rehearse and perform musical pieces.}
        \item {Filled in for the director at rehearsals.}
        \item {Conducted the pit orchestra for school musicals.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Drum Major of Marching Band} % Affiliation/role
    {} % Organization/group
    {} % Location
    {2008 - 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Taught musical pieces for bi-weekly marching band performances at the football half-time show.}
        \item {Wrote and taught drill (marching band formations and transitions) for performances.}
        \item {Mentored 6 years of new drum majors.}
      \end{cvitems}
    }

      \cventry
    {Performer} % Affiliation/role
    {} % Organization/group
    {} % Location
    {2007 - 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Played oboe and clarinet in the Concert Band and Orchestra.}
        \item {Played piano for the Jazz Band and Jazz Combo.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {President \& Vice President} % Affiliation/role
    {Society of Geophysics Graduate Students} % Organization/group
    {Golden, Colorado} % Location
    {2013-2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Graduate student representative on the Graduate Admissions Council, reviewed applications of incoming graduate students.}
        \item {Representative of the Geophysics Department on the Graduate Student Government.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Xi Chapter Member \& Vice President} % Affiliation/role
    {Kappa Kappa Psi, Honorary Band Fraternity} % Organization/group
    {Golden, Colorado} % Location
    {2007-2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Coordinated fundraisers to support the CSM Music Department.}
        \item {Organized service events to build and repair equipment for the music department.}
        \item {Volunteered to teach high school and grade school students music lessons.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
